\vspace{0.3em}
\subsection{{Kaggle Hackathon Honorable Mention
 (8/321) - \href{https://www.kaggle.com/competitions/google-tunix-hackathon/writeups/new-writeup-1763082571151}{[Solution Write-up]} \hfill May 2026}}
\textcolor{darkgray}{
Fine-tuned Gemma 2 2B Instruct for reasoning with a curated data mixture, LoRA reasoning SFT, and DPO based on the Delta Learning Hypothesis. Trained on Google TPU.
}
\vspace{0.3em}

\subsection{{Kaggle Competition Master (Ranked 842 worldwide; 1x Gold, 2x Silver). \hfill Feb 2026}}
\vspace{0.3em}
\subsection{{Kaggle Competition Gold Medal (13/3357) - \href{https://www.kaggle.com/competitions/santa-2025/writeups/13th-place-santa25-billiard-customized-sparrow}{[Solution Write-up]} \hfill Feb 2026}}
\textcolor{darkgray}{
Built a Rust solver for irregular 2D bin packing, placing non-convex shapes into the smallest possible bounding square across hundreds of configurations. Combined simulated annealing, local search, and constraint relaxation over the 3-month competition.
}
\vspace{0.3em}
\subsection{{Kaggle Competition Silver Medal (19/1151) - Presented at NeurIPS 2025 Special Session\href{https://docs.google.com/presentation/d/1dnbbxxKHlpp_7AG-3h-olI2iJIY0TT0t_pmanXiiiCs/edit?usp=sharing}{\ [Solution Presentation]}\hfill Oct 2025}}
\textcolor{darkgray}{
Built a program-synthesis agent with an evolutionary database to solve ARC-AGI tasks while optimizing for minimal code length.}
% The competition featured both human-submitted and agentic solutions; the top three teams are all expert human code golfers. }
% Placed only five positions behind Frontier AI Lab Sakana AI’s ALE agent and one position behind NVIDIA's Kaggle Grandmaster team.}
\vspace{0.3em}

\vspace{0.3em}

\subsection{{Mistral AI Award - Hack the Law Hackathon \hfill Jun 2025}}
\textcolor{darkgray}{
Built a Mixtral-based multi-agent system to extract, classify, and link regulated activities and entities from legal documents.
}
\vspace{0.3em}

\subsection{{1\textsuperscript{st} Place - Infosys Cambridge AI Centre Hackathon \hfill May 2025}}
\textcolor{darkgray}{
Built \href{https://github.com/Yuchen20/Memory-Plus}{\textbf{Memory Plus}}, an MCP memory layer for LLMs with a local vector store and RAG. (\textbf{50+ GitHub stars; 8k downloads})
}

% \subsection{{2\textsuperscript{nd} Place – Cambridge Neuphonic Hackathon  \hfill Jan 2025}}
% % \textcolor{darkgray}{
% % Built an AI-powered Dungeons \& Dragons game using \textbf{Gemini's context caching} for efficient game world persistence and \textbf{structured outputs} to present real-time player statistics.} 
% \href{https://www.linkedin.com/feed/update/urn:li:ugcPost:7287253032365424640?commentUrn=urn%3Ali%3Acomment%3A%28ugcPost%3A7287253032365424640%2C7287926422742953985%29&dashCommentUrn=urn%3Ali%3Afsd_comment%3A%287287926422742953985%2Curn%3Ali%3AugcPost%3A7287253032365424640%29}{\textbf{Endorsed by Neuphonic CTO:} Absolute machine as a one-man project!! }
