%**====================**
%** EXPERIENCE A**
%**====================**
\subsection{{Viridien | \textcolor{darkgray}{Machine Learning Engineer} \hfill 2025/08 -- Present}}
\begin{zitemize}
\item \textbf{VLM document classification}: \textcolor{darkgray}{Fine-tuned vision-language models for oil \& gas technical documents using LoRA SFT, RLVR methods (GRPO/GSPO), and prompt optimization with ACE-Agent and DSPy. Improved F1 / accuracy from 0.47 / 0.74 to 0.78 / 0.85 at comparable model size.}
\item \textbf{Agentic Label QC System}: \textcolor{darkgray}{Built an agentic QC system through close collaboration with domain experts. Translated expert feedback into agents improvements, incorporating vision capabilities, expert-written skills for domain knowledge injection, and a critic-validator framework to improve label reliability.}
\item \textbf{Agent terminal-use training}: \textcolor{darkgray}{Done Reinfrocement Learning on Qwen models on multi-GPU infrastructure with Harbor, SGLang, and AREAL to improve terminal-use behavior, in collaboration with CAMEL-AI.}
\end{zitemize}

\subsection{{Autodesk | \textcolor{darkgray}{Intern, Technology Consultant (AI/ML)} \hfill 2024/06 -- 2024/09}}
\begin{zitemize}
\item \textbf{VLM benchmarking for CAM}: \textcolor{darkgray}{Created a benchmark dataset for evaluating how vision-language models understand Computer-Aided Manufacturing workflows. The benchmark supported model selection for Fusion agents and gives the team a repeatable way to test new model releases.}
\end{zitemize}

%**====================**
%** EXPERIENCE B**
%**====================**

\subsection{{Business-Intelligence of Oriental Nations Corporation Ltd | \textcolor{darkgray}{Intern, Algorithm Engineer} \hfill 2023/06 -- 2023/09}}
\begin{zitemize}
\item \textbf{Manufacturing ML}: \textcolor{darkgray}{Trained machine learning models for manufacturing applications using scikit-learn and XGBoost.}
\end{zitemize}

